My title

### 2023-03-20 outputs/paper/paper.qmd
add tests and simulate the data

```{r,echo=FALSE}
cleaned_data <- read_csv(
  file = here("inputs/data/GSS2021 2.csv"))
```

@@

```{r}
#| label: fig-bills1
#| fig-cap: Bills of penguins
#| echo: false

@@

# # Rename the column names
# col_names <- c("Term", "Estimate", "Std. Error", "t value", "Pr(>|t|)")
# colnames(summary_df) <- col_names
# 
# # Print the summary table with kableExtra
# library(kableExtra)
# kable(summary_df, align = c("l", "r", "r", "r", "r"), 
#       caption = "Summary of Linear Regression Model",) %>%
#   kable_styling(bootstrap_options = "striped", full_width = FALSE)

```
```{r}
#| label: fig-billssssss0
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

@@

tb1%>%kable(booktabs = TRUE)
```

```{r}
#| label: fig-billssssss2
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(data = cleaned_data, aes(x = educ)) +

@@

```{r}
#| label: fig-billssssss3
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = mapres10)) +
  geom_histogram(aes(y = ..density.., fill = "mapres10"), alpha = 1, binwidth = 2,color = "black") +
  geom_histogram(aes(x = papres10, y = ..density.., fill = "paeduc"), alpha = 0.4, binwidth = 2,color = "black") +
  scale_fill_manual(values = c("mapres10" = "lightblue", "paeduc" = "red"), name = "Variables") +
  labs(title = "Difference between Mother's and Father's Prestige Score",
       x = "Prestige Score",
       y = "Density")+
  theme_bw()
```

```{r}
#| label: fig-billssssss4
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = maeduc)) +
  geom_histogram(aes(y = ..density.., fill = "maeduc"), alpha = 1, binwidth = 1, color = "black") +
  geom_histogram(aes(x = paeduc, y = ..density.., fill = "paeduc"), alpha = 0.4, binwidth = 1, color = "black") +
  scale_fill_manual(values = c("maeduc" = "lightblue", "paeduc" = "red"), name = "Variables") +
  labs(title = "Differene between Mother's Education and Father's Education",
       x = "Education (in Years)",
       y = "Density") +
  theme_bw()
```

@@

```{r}
#| label: fig-billssssss5
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

@@

```{r}
#| label: fig-billssssss6
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ,fill = factor(reg16))) +
  geom_histogram(binwidth = 2, color = "black") +
  facet_wrap(~ reg16, ncol = 3)+
  labs(title = "Respondent's Living Region at Age of 16 v.s. Education",
       x = "Education (in Years)",
       y = "Count")+
  theme_bw()+
  theme(legend.position = "none")
```

```{r}
#| label: fig-billssssss7
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

```

@@

## Weaknesses and next steps
*problems with prestige score:*
Subjectivity: Even measures of prestige that attempt to capture objective indicators of social status, such as income or educational attainment, are still subject to subjective interpretation. People's perceptions of what constitutes a high-prestige occupation may vary based on their own cultural, social, or personal biases.

>>>>

```{r,echo=FALSE}
#| include: false
#| warning: false
#| message: false
cleaned_data <- read_csv(
  file = here("inputs/data/GSS2021 2.csv"))
```

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-2021-gender
#| tbl-cap: Linear Model and its Summary Statistics

@@

# Rename the column names
col_names <- c("Term", "Estimate", "Std. Error", "t value", "Pr(>|t|)")
colnames(summary_df) <- col_names

# Print the summary table with kableExtra
library(kableExtra)
kable(summary_df, align = c("l", "r", "r", "r", "r"),
      caption = "Summary of Linear Regression Model")
```
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-degree
#| tbl-cap: Respondents' Degree in 2021 Survey

@@

tb1%>%kable()
```

```{r}
#| label: fig-educ
#| fig-cap: Histogram of Respondents' Education
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(data = cleaned_data, aes(x = educ)) +

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-educationyears
#| tbl-cap: Number of respondents by gender for 2021 survey
tb0 <- cleaned_data %>% summarise(Min = min(cleaned_data$educ,na.rm=T),
                              Median = median(cleaned_data$educ,na.rm=T),
                              Max = max(cleaned_data$educ,na.rm = T),
                              Mean = mean(cleaned_data$educ,na.rm=T))

tb0%>%kable()
```

```{r}
#| label: fig-parentpre
#| fig-cap: Mother's and Father's Prestige Score
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
# ggplot(cleaned_data, aes(x = mapres10)) +
#   geom_histogram(aes(y = ..density.., fill = "mapres10"), alpha = 1, binwidth = 2,color = "black") +
#   geom_histogram(aes(x = papres10, y = ..density.., fill = "paeduc"), alpha = 0.8, binwidth = 2,color = "black") +
#   scale_fill_manual(values = c("mapres10" = "lightblue", "paeduc" = "darkred"), name = "Variables") +
#   labs(title = "Mother's and Father's Prestige Score",
#        x = "Prestige Score",
#        y = "Density")+
#   theme_bw()

##edit this
ggplot(cleaned_data, aes(x = mapres10)) +
  geom_histogram(aes(y = ..density.., fill = "Mother's Prestige Score"), alpha = 1, binwidth = 1, color = "black")+
  geom_histogram(aes(x = papres10, y = ..density.., fill = "Father's Prestige Score"), alpha = 0.8, binwidth = 1, color = "black") +
  scale_fill_manual(values = c("Mother's Prestige Score" = "darkgreen", "Father's Prestige Score" = "lightgreen"), name = "Variables") +
  labs(title = "Mother's and Father's Prestige Score",
       x = "Prestige Score",
       y = "Density") +
  theme_bw()
```

```{r}
#| label: fig-parentseduc
#| fig-cap: Mother's Education and Father's Education Level
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = maeduc)) +
geom_histogram(aes(y = ..density.., fill = "Mother's Education"), alpha = 1, binwidth = 0.5, color = "black") +
geom_histogram(aes(x = paeduc, y = ..density.., fill = "Father's Education"), alpha = 0.8, binwidth = 0.5, color = "black") +
scale_fill_manual(values = c("Mother's Education" = "darkgreen", "Father's Education" = "lightgreen"), name = "Variables") +
labs(title = "Mother's Education and Father's Education Level",
x = "Education (in Years)",
y = "Density") +
theme_bw()
```

@@

```{r}
#| label: fig-birth
#| fig-cap: Birthplace of the Respondent \n (if outside of US)
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4

@@

```{r}
#| label: fig-region
#| fig-cap: Respondent's Living Region at Age of 16 v.s. Education
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ,fill = factor(reg16))) +
  geom_histogram(binwidth = 2, color = "black") +
  facet_wrap(~ reg16, ncol = 3)+
  labs(title = "Respondent's Living Region at Age of 16 v.s. Education",
       x = "Education (in Years)",
       y = "Count")+
  theme_bw()+
  theme(legend.position = "none")
```

```{r}
#| label: fig-maincome
#| fig-cap: Education vs Mother's Education with respect to Family Income
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ, y = maeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Mother's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Mother's Educaion (in Years)",
       color = "Family Income \n (at Age of 16)") +
  scale_color_discrete(name = "Family Income \n (at Age of 16)") +
  theme_bw()
```

```{r}
#| label: fig-paincome
#| fig-cap: Education vs Father's Education with respect to Family Income
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ, y = paeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Father's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Father's Educaion (in Years)",
  color = "Family Income \n (at Age of 16)") +
  scale_color_discrete(name = "Family Income \n (at Age of 16)") +
  theme_bw()
```

@@

## Weaknesses and next steps {#sec-weaknesses}
*problems with prestige score:*
Subjectivity: Even measures of prestige that attempt to capture objective indicators of social status, such as income or educational attainment, are still subject to subjective interpretation. People's perceptions of what constitutes a high-prestige occupation may vary based on their own cultural, social, or personal biases.
